\textsc{Does Copyright Affect Reuse?\\ Evidence from Wikipedia and the Google Books Digitization Project}

### 2016-09-30 writing/paper.tex
before Lisa edits

\usepackage[letterpaper,left=1in,right=1in,top=1.4in,bottom=1.5in]{geometry}

% packages i use in essentially every document
\usepackage{graphicx}
\usepackage{enumerate}
\usepackage{booktabs}
\usepackage{lipsum}
\usepackage{lscape}
\usepackage{dcolumn}
\usepackage{amsmath}
\usepackage{comment}

@@

\linespread{1.2}

@@

\begin{abstract}
\normalsize
While digitization projects like Google Books have dramatically increased access to information, this study examines how the ability to reuse digital information and diffuse knowledge to a wider audience critically depends on features of copyright law. I use the digitization of both copyrighted and non-copyrighted issues of \emph{Baseball Digest} by the Google Books Digitization Project to measure the impact of copyright on a prominent venue for reuse: Wikipedia. A specific feature of the 1909 Copyright Act, \emph{copyright renewal requirements} ensure that material published before 1964 is out of copyright, which allows for causal estimation of the impact of copyright on Wikipedia across this sharp cutoff. I find that digitization by Google Books increased the reuse of Baseball Digest on Wikipedia, but copyright hurt reuse by reducing citations to copyrighted issues by over 135\%. Copyright also had real impacts on readership -- affected pages had, on average, 20\% lower gains in internet traffic than pages unaffected by copyright. Finally, the impact of copyright on digitized material was highly uneven. Copyright mostly affected the reuse of images rather than text, and prevented reuse of information about less-popular players as compared to more popular ones. 
\end{abstract}

>>>>

\usepackage[letterpaper,left=1in,right=1in,top=1in,bottom=1in]{geometry}

% packages i use in essentially every document
\usepackage{graphicx}
\usepackage{enumerate}
\usepackage{booktabs}
\usepackage{lipsum}
\usepackage{lscape}
\usepackage{dcolumn}
\usepackage{amsmath}
\usepackage{comment}
\usepackage{setspace}
\usepackage{mathptmx}

@@

\linespread{1.5}

@@

\begin{abstract}
\normalsize
\setstretch{1.2}

While digitization projects like Google Books have dramatically increased access to information, this study examines how the ability to reuse digital information and diffuse knowledge to a wider audience critically depends on features of copyright law. I use the digitization of both copyrighted and non-copyrighted issues of \emph{Baseball Digest} by the Google Books Digitization Project to measure the impact of copyright on a prominent venue for reuse: Wikipedia. A specific feature of the 1909 Copyright Act, \emph{copyright renewal requirements} ensure that material published before 1964 is out of copyright, which allows for causal estimation of the impact of copyright on Wikipedia across this sharp cutoff. I find that digitization by Google Books increased the reuse of Baseball Digest on Wikipedia, but copyright hurt reuse by reducing citations to copyrighted issues by over 135\%. Copyright also had real impacts on readership -- affected pages had, on average, 20\% lower gains in internet traffic than pages unaffected by copyright. Finally, the impact of copyright on digitized material was highly uneven. Copyright mostly affected the reuse of images rather than text, and prevented reuse of information about less-popular players as compared to more popular ones. 
\end{abstract}
